---
title: "Character Conversational Network (Series)"
author: "Alyssa April Dellow"
date: "21 April 2026"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Libraries

```{r libraries, message = FALSE, warning = FALSE}
library(readxl) # to import the data in Excel to R
library(igraph) # for network analysis
library(dplyr) # to use pipe operator
library(ggplot2)
library(sna)
library(tidyr)
```
### Set Gender Shape, Race Colour and Edge Colour (Relationship) for the Series

```{r series details, echo = FALSE}
details <- read_excel("E:/PhD Year 1/Upin Ipin/BMMSS Data, Code, Figures/BMMSS Data/Series Stats Season 1 and Season 2.xlsx",
                             sheet = 4) # load Excel sheet of characters, gender and race into R

df_details <- data.frame(details)

colour <- c("tan1", "lightblue", "plum", "pink", "grey", "yellow") # six different colours for Malay, Chinese, Indian, Sikh, Unknown and Animal

relay_details <- read_excel("E:/PhD Year 1/Upin Ipin/BMMSS Data, Code, Figures/BMMSS Data/Series Stats Season 1 and Season 2.xlsx", sheet = 3) # load Excel sheet of nodes and relationships

df_relay <- data.frame(relay_details)

relay <- c("wheat4", "seagreen3", "red") # three different colours for good/neutral relationship, family and bad relationship

# set the colour for each node according to their race
race_levels <- unique(df_details$Race)
race_colour <- setNames(colour[seq_along(race_levels)], race_levels)

# set the shape for each node according to their gender
gender_levels <- unique(df_details$Gender)
gender_shape <- setNames(c("circle", "square", "triangle")[seq_along(gender_levels)], gender_levels)

# set the colour for each edge according to the type of relationship between the pair of nodes
relationship_levels <- unique(df_relay$Relationship)
relay_colour <- setNames(relay[seq_along(relationship_levels)], relationship_levels)
```

### Creating the Directed Network for Series and Plotting it

```{r network, message = FALSE, warning = FALSE}

# read edge list 
edges_dir <- read_excel("E:/PhD Year 1/Upin Ipin/BMMSS Data, Code, Figures/BMMSS Data/Series Stats Season 1 and Season 2.xlsx", sheet = "Final")
  
# read node details
nodes <- read_excel("E:/PhD Year 1/Upin Ipin/BMMSS Data, Code, Figures/BMMSS Data/Series Stats Season 1 and Season 2.xlsx", sheet = "Details")
  
# Create an igraph object
series_net <- graph_from_data_frame(d = edges_dir, vertices = nodes, directed = TRUE)

series_adj <- as.matrix(get.adjacency(series_net, attr = "Weight"))
```

### Plotting the Undirected Network

```{r undirected network, echo = FALSE, fig.height = 20, fig.width = 20, out.width = "100%"}

# read edge list 
edges_dir1 <- read_excel("E:/PhD Year 1/Upin Ipin/BMMSS Data, Code, Figures/BMMSS Data/Series Stats Season 1 and Season 2.xlsx", sheet = "Undirected")

series_net_undirected <- graph_from_data_frame(d = edges_dir1, vertices = nodes, directed = FALSE)

series_adj_undirected <- as.matrix(get.adjacency(series_net_undirected))

plot(series_net_undirected,
     layout = layout_nicely(series_net_undirected),
     vertex.size = 11,
     vertex.color = race_colour[V(series_net_undirected)$Race],
     vertex.shape = gender_shape[V(series_net_undirected)$Gender],
     vertex.frame.color = "black",
     vertex.label = V(series_net_undirected)$name,
     vertex.label.cex = 1.7,
     vertex.label.color = "black",
     edge.color = relay_colour[E(series_net_undirected)$Relationship],
     edge.width = 4,
     edge.arrow.size = 1.5,
     edge.curved = 0.3)
```

```{r series plot, echo = FALSE, fig.height = 20, fig.width = 20, out.width = "100%"}

set.seed(10)

# plot directed network
plot(series_net, 
     layout = layout_nicely(series_net),
     vertex.size = 11, 
     vertex.color = race_colour[V(series_net)$Race], 
     vertex.shape = gender_shape[V(series_net)$Gender],
     vertex.frame.color = "black", 
     vertex.label = V(series_net)$name, 
     vertex.label.cex = 1.7, 
     vertex.label.color = "black", 
     edge.color = relay_colour[E(series_net)$Relationship], 
     edge.width = abs(E(series_net)$Weight)*0.6,
     edge.arrow.size = 1.5,
     edge.curved = 0.3)

# add legend for node colours (Race)
legend(x = 0.9, y = 1.1, legend = names(race_colour), 
       col = race_colour, pch = 16, pt.cex = 4, cex = 1.9, bty = "n", title = "Race")

# add legend for node shapes (Gender)
legend(x = 0.9, y = 0.795, legend = c("Male", "Female"),
       pch = c(16, 15, 17), pt.cex = 4, cex = 1.9, bty = "n", title = "Gender")

# add legend for edge colours (Relationship)
legend(x = 0.9, y = 0.58, legend = c("Family", "Good"), 
       col = relay_colour, lty = 1, lwd = 8, cex = 1.9, bty = "n", title = "Relationship")
```

### Centrality Measures for Series (Directed and Weighted Degree Centrality)

```{r centrality}

# degree centrality (total weight in and out divided by sum of all weight multiply by 2)
series_deg <- degree(series_adj, rescale = TRUE)
names(series_deg) <- rownames(series_adj)  # Assign names (if rownames exist)
deg_sorted_role <- sort(series_deg, decreasing = TRUE)  # Sort in decreasing order
print(deg_sorted_role)

```

# Centralities for Undirected and Unweighted Network

```{r centrality undirected and Unweighted}

# degree centrality (total weight in and out divided by sum of all weight multiply by 2)
series_deg <- degree(series_adj_undirected, gmode = "graph", rescale = TRUE)
names(series_deg) <- rownames(series_adj)  # Assign names (if rownames exist)
deg_sorted <- sort(series_deg, decreasing = TRUE)  # Sort in decreasing order
print(deg_sorted)

# eigenvector centrality
series_eigen <- eigen_centrality(series_net_undirected)
eigen_sorted <- sort(series_eigen$vector, decreasing = TRUE)
print(eigen_sorted)

# betweenness centrality 
# invert the weight since weight is interpreted as distances
series_btwn <- betweenness.estimate(series_net_undirected, directed = FALSE, cutoff = -1)
btwn_sorted <- sort(series_btwn, decreasing = TRUE)
print(btwn_sorted)

# closeness centrality
series_closeness <- closeness.estimate(series_net_undirected, mode = "all", cutoff = -1)
closeness_sorted <- sort(series_closeness, decreasing = TRUE)
print(closeness_sorted)
```

### Graph Details

```{r deets}

desc_series_net <- cbind(gsize(series_net), gsize(series_net_undirected),
                    transitivity(series_net_undirected, type = "global"), # this is undirected and unweighted
                    mean_distance(series_net, E(series_net)$Weight),
                    mean_distance(series_net),
                    mean_distance(series_net_undirected, directed = FALSE),
                    edge_density(series_net_undirected))

paste("Number of Edges Directed:", desc_series_net[1],
      "Number of Edges Undirected:", desc_series_net[2],
      "GCC Undirected and Unweighted:", desc_series_net[3], 
      "Average Path Length Directed and Weighted:", desc_series_net[4],
      "Average Path Length Directed and Unweighted:", desc_series_net[5],
      "Average Path Length Undirected and Unweighted:", desc_series_net[6],
      "Density:", desc_series_net[7])
```

### Community Detection

```{r community detection, echo = FALSE, fig.height = 20, fig.width = 20, out.width = "100%"}

# Walktrap
wc <- cluster_walktrap(series_net, weights = E(series_net)$Weight)
membership(wc) # obtain the membership of each node
modularity(wc, weights = E(series_net)$Weight)

set.seed(10)

# export figure as PNG
png(
  filename = "Fig1(a).png",
  width = 6.85, # 174 mm in inches
  height = 7.5,   # less than 234 mm
  units = "in",
  res = 1200 # 1200dpi resolution
)

par(family = "sans", mar = c(1, 1, 1, 1)) # set font and margins

# plot directed network with community detection
plot(wc, series_net, 
     layout = layout_nicely(series_net),
     vertex.size = 14, 
     vertex.label.family = "sans", # font
     col = race_colour[V(series_net)$Race], 
     vertex.shape = gender_shape[V(series_net)$Gender],
     vertex.frame.color = "black", 
     vertex.label = V(series_net)$name, 
     vertex.label.cex = 0.8, 
     vertex.label.color = "black", 
     edge.color = relay_colour[E(series_net)$Relationship], 
     edge.width = abs(E(series_net)$Weight)*0.4,
     edge.arrow.size = 0.6,
     edge.curved = 0.3)

# add legend for node colours (Race)
legend(x = 0.7, y = 1.1, legend = names(race_colour), 
       col = race_colour, pch = 16, pt.cex = 1.8, cex = 0.8, bty = "n", title = "Race")

# add legend for node shapes (Gender)
legend(x = 0.7, y = 0.7, legend = c("Male", "Female"),
       pch = c(16, 15, 17), pt.cex = 1.8, cex = 0.8, bty = "n", title = "Gender")

# add legend for edge colours (Relationship)
legend(x = 0.7, y = 0.4, legend = c("Family", "Good"), 
       col = relay_colour, lty = 1, lwd = 3, cex = 0.8, bty = "n", title = "Relationship")

dev.off()
```

### Major, Minor and Extra Role Classification based on Weighted and Directed Degree Centrality

```{r major, minor, extra roles}

# put the character names and their normalised degree values in a dataframe
deg_names <- names(deg_sorted_role)
names(deg_sorted_role) <- NULL
deg_df <- data.frame(Name = deg_names, Degree = deg_sorted_role)

# compute the average degree
avg_deg <- mean(deg_df$Degree)

# extras are those who have a degree value less than the average degree
extra_role <- deg_df[deg_df$Degree < avg_deg, ]

# major and minor roles
maj_min <- deg_df[deg_df$Degree >= avg_deg, ]

# find the biggest gap between major and minor nodes
gaps <- abs(diff(maj_min$Degree))
max_gap <- which.max(gaps)

# classify the characters
maj_min$Role <- "Minor"
maj_min$Role[1:max_gap] <- "Major"
extra_role$Role <- "Extra"

# combine all the characters into a single df
role_df <- rbind(maj_min, extra_role)
role_df$Role <- factor(role_df$Role, levels = c("Major", "Minor", "Extra"))
role_df$Name <- factor(role_df$Name, levels = role_df$Name)

role_df_corr <- role_df # for use in correlation analysis section

png("Fig2(a).png", width = 6.85, height = 6, units = "in", res = 1200, family = "sans") # save png for submission

# plot the classification of roles
ggplot(role_df, aes(x = Name, y = Degree, color = Role, shape = Role, group = 1)) +
  geom_line(linewidth = 1) +  # line connecting the points
  geom_point(size = 3) +  # dots of each character
  geom_hline(yintercept = avg_deg, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # average degree centrality line
  geom_vline(xintercept = max_gap + 0.5, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # largest gap line
  annotate("text", x = length(role_df$Name)/2 + 2, y = avg_deg + 0.008, label = "Average Degree", color = "black", size = 5) +  # label for avg degree
  annotate("text", x = max_gap + 1, y = max(role_df$Degree) - 0.05, label = "Largest Gap", color = "black", size = 5, angle = 270) +  # label for largest gap
  scale_color_manual(values = c("green", "blue", "red")) +  # colours for Major, Minor, Extra
  scale_shape_manual(values = c(16, 17, 15)) +  # shapes for Major, Minor, Extra
  theme_minimal(base_family = "sans") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = "black"),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  labs(x = "Series Characters",
       y = "Degree Centrality",
       color = "Role",
       shape = "Role") 

dev.off()
```

### Role Classification (Unweighted and Undirected Degree)

```{r major, minor, extra roles - degree undirected unweighted}

# put the character names and their degree values in a dataframe
deg_unw_und_names <- names(deg_sorted)
names(deg_sorted) <- NULL
deg_unw_und_df <- data.frame(Name = deg_unw_und_names, Degree = deg_sorted)

# compute the average degree
avg_deg_unw_und <- mean(deg_unw_und_df$Degree)

# extras are those who have a degree value less than the average degree
extra_role <- deg_unw_und_df[deg_unw_und_df$Degree < avg_deg_unw_und, ]

# major and minor roles
maj_min <- deg_unw_und_df[deg_unw_und_df$Degree >= avg_deg_unw_und, ]

# find the biggest gap between major and minor nodes
gaps <- abs(diff(maj_min$Degree))
max_gap <- which.max(gaps)

# classify the characters
maj_min$Role <- "Minor"
maj_min$Role[1:max_gap] <- "Major"
extra_role$Role <- "Extra"

# combine all the characters into a single df
role_df <- rbind(maj_min, extra_role)
role_df$Role <- factor(role_df$Role, levels = c("Major", "Minor", "Extra"))
role_df$Name <- factor(role_df$Name, levels = role_df$Name)

png("Fig7(a).png", width = 6.85, height = 6, units = "in", res = 1200, family = "sans")

# plot the classification of roles
ggplot(role_df, aes(x = Name, y = Degree, color = Role, shape = Role, group = 1)) +
  geom_line(linewidth = 1) +  # line connecting the points
  geom_point(size = 3) +  # dots of each character
  geom_hline(yintercept = avg_deg_unw_und, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # average deg centrality line
  geom_vline(xintercept = max_gap + 0.5, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # largest gap line
  annotate("text", x = length(role_df$Name)/2 + 4.8, y = avg_deg_unw_und + 0.009, label = "Average Degree \n(Undirected & Unweighted)", color = "black", size = 4) +  # label for avg degree
  annotate("text", x = max_gap + 0.9, y = max(role_df$Degree) - 0.01, label = "Largest Gap", color = "black", size = 4, angle = 270) +  # label for largest gap
  scale_color_manual(values = c("green", "blue", "red")) +  # colours for Major, Minor, Extra
  scale_shape_manual(values = c(16, 17, 15)) +
  scale_y_continuous(limits = c(0, 0.15)) +
  theme_minimal(base_family = "sans") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), 
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = "black"),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  labs(x = "Series Characters",
       y = "Degree Centrality (Undirected & Unweighted)",
       color = "Role",
       shape = "Role") 

dev.off()
```

### Role Classification (Eigenvector)

```{r major, minor, extra roles - eigenvector}

# put the character names and their eigenvector values in a dataframe
ev_names <- names(eigen_sorted)
names(eigen_sorted) <- NULL
ev_df <- data.frame(Name = ev_names, Eigenvector = eigen_sorted)

# compute the average eigenvector
avg_ev <- mean(ev_df$Eigenvector)

# extras are those who have a ev value less than the average ev
extra_role <- ev_df[ev_df$Eigenvector < avg_ev, ]

# major and minor roles
maj_min <- ev_df[ev_df$Eigenvector >= avg_ev, ]

# find the biggest gap between major and minor nodes
gaps <- abs(diff(maj_min$Eigenvector))
max_gap <- which.max(gaps)

# classify the characters
maj_min$Role <- "Minor"
maj_min$Role[1:max_gap] <- "Major"
extra_role$Role <- "Extra"

# combine all the characters into a single df
role_df <- rbind(maj_min, extra_role)
role_df$Role <- factor(role_df$Role, levels = c("Major", "Minor", "Extra"))
role_df$Name <- factor(role_df$Name, levels = role_df$Name)

png("Fig7(c).png", width = 6.85, height = 6, units = "in", res = 1200, family = "sans")

# plot the classification of roles
ggplot(role_df, aes(x = Name, y = Eigenvector, color = Role, shape = Role, group = 1)) +
  geom_line(linewidth = 1) +  # line connecting the points
  geom_point(size = 3) +  # dots of each character
  geom_hline(yintercept = avg_ev, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # average ev centrality line
  geom_vline(xintercept = max_gap + 0.5, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # largest gap line
  annotate("text", x = length(role_df$Name)/2 + 5, y = avg_ev + 0.03, label = "Average Eigenvector", color = "black", size = 4.2) +  # label for avg ev
  annotate("text", x = max_gap + 0.9, y = max(role_df$Eigenvector) - 0.5, label = "Largest Gap", color = "black", size = 4.2, angle = 270) +  # label for largest gap
  scale_color_manual(values = c("green", "blue", "red")) +  # colours for Major, Minor, Extra
  scale_shape_manual(values = c(16, 17, 15)) +
  theme_minimal(base_family = "sans") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), 
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = "black"),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  labs(x = "Series Characters",
       y = "Eigenvector Centrality",
       color = "Role",
       shape = "Role")

dev.off()
```

### Role Classification (Betweenness)

```{r major, minor, extra roles - betweenness}

# put the character names and their betweenness values in a dataframe
btwn_names <- names(btwn_sorted)
names(btwn_sorted) <- NULL
btwn_df <- data.frame(Name = btwn_names, Betweenness = btwn_sorted)

# compute the average betweenness
avg_btwn <- mean(btwn_df$Betweenness)

# extras are those who have a btwn value less than the average btwn
extra_role <- btwn_df[btwn_df$Betweenness < avg_btwn, ]

# major and minor roles
maj_min <- btwn_df[btwn_df$Betweenness >= avg_btwn, ]

# find the biggest gap between major and minor nodes
gaps <- abs(diff(maj_min$Betweenness))
max_gap <- which.max(gaps)

# classify the characters
maj_min$Role <- "Minor"
maj_min$Role[1:max_gap] <- "Major"
extra_role$Role <- "Extra"

# combine all the characters into a single df
role_df <- rbind(maj_min, extra_role)
role_df$Role <- factor(role_df$Role, levels = c("Major", "Minor", "Extra"))
role_df$Name <- factor(role_df$Name, levels = role_df$Name)

png("Fig7(e).png", width = 6.85, height = 6, units = "in", res = 1200, family = "sans")

# plot the classification of roles
ggplot(role_df, aes(x = Name, y = Betweenness, color = Role, shape = Role, group = 1)) +
  geom_line(linewidth = 1) +  # line connecting the points
  geom_point(size = 3) +  # dots of each character
  geom_hline(yintercept = avg_btwn, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # average btwn centrality line
  geom_vline(xintercept = max_gap + 0.5, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # largest gap line
  annotate("text", x = length(role_df$Name)/2 - 0.5, y = avg_btwn + 0.6, label = "Average Betweenness", color = "black", size = 5) +  # label for avg btwn
  annotate("text", x = max_gap + 0.9, y = max(role_df$Betweenness) - 5, label = "Largest Gap", color = "black", size = 5, angle = 270) +  # label for largest gap
  scale_color_manual(values = c("green", "blue", "red")) +  # colours for Major, Minor, Extra
  scale_shape_manual(values = c(16, 17, 15)) +
  theme_minimal(base_family = "sans") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), 
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = "black"),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  labs(x = "Series Characters",
       y = "Betweenness Centrality",
       color = "Role",
       shape = "Role") 

dev.off()
```

### Role Classification (Closeness)

```{r major, minor, extra roles - closeness}

# put the character names and their closeness values in a dataframe
closeness_names <- names(closeness_sorted)
names(closeness_sorted) <- NULL
closeness_df <- data.frame(Name = closeness_names, Closeness = closeness_sorted)

# compute the average closeness
avg_closeness <- mean(closeness_df$Closeness)

# extras are those who have a closeness value less than the average closeness
extra_role <- closeness_df[closeness_df$Closeness < avg_closeness, ]

# major and minor roles
maj_min <- closeness_df[closeness_df$Closeness >= avg_closeness, ]

# find the biggest gap between major and minor nodes
gaps <- abs(diff(maj_min$Closeness))
max_gap <- which.max(gaps)

# classify the characters
maj_min$Role <- "Minor"
maj_min$Role[1:max_gap] <- "Major"
extra_role$Role <- "Extra"

# combine all the characters into a single df
role_df <- rbind(maj_min, extra_role)
role_df$Role <- factor(role_df$Role, levels = c("Major", "Minor", "Extra"))
role_df$Name <- factor(role_df$Name, levels = role_df$Name)

png("Fig7(g).png", width = 6.85, height = 6, units = "in", res = 1200, family = "sans")

# plot the classification of roles
ggplot(role_df, aes(x = Name, y = Closeness, color = Role, shape = Role, group = 1)) +
  geom_line(linewidth = 1) +  # line connecting the points
  geom_point(size = 3) +  # dots of each character
  geom_hline(yintercept = avg_closeness, linetype = "dotted", color = "darkgrey", linewidth = 1) + # avg closeness centrality line
  geom_vline(xintercept = max_gap + 0.5, linetype = "dotted", color = "darkgrey", linewidth = 1) +  # largest gap line
  annotate("text", x = length(role_df$Name)/2 + 4.3, y = avg_closeness + 0.002, label = "Average Closeness", color = "black", size = 5) +  # label for avg closeness
  annotate("text", x = max_gap + 1.35, y = max(role_df$Closeness) + 0.0035, label = "Largest \nGap", color = "black", size = 5, angle = 270) +  # label for largest gap
  scale_color_manual(values = c("green", "blue", "red")) +  # colours for Major, Minor, Extra
  scale_shape_manual(values = c(16, 17, 15)) +
  scale_y_continuous(limits = c(0.03, 0.08)) +
  theme_minimal(base_family = "sans") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), 
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = "black"),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 15)) +
  labs(x = "Series Characters",
       y = "Closeness Centrality",
       color = "Role",
       shape = "Role") 

dev.off()
```

### Correlation Analysis Between Ordinal Roles / Weighted DC and Unweighted DC, EC, BC, CC

```{r spearman and kendall}
# spearman and kendall tau correlations to compare the major/minor/extra classification roles 
# with the other centrality measures

# combine all centrality measures into one dataframe
all_centralities <- data.frame(
  Name = names(series_deg),
  Degree = as.numeric(series_deg),
  Eigenvector = as.numeric(series_eigen$vector[names(series_deg)]),
  Betweenness = as.numeric(series_btwn[names(series_deg)]),
  Closeness = as.numeric(series_closeness[names(series_deg)])
)

# merge role classification with all the other centralities
combined_df <- merge(all_centralities, role_df_corr, by = "Name")

combined_df <- combined_df %>%
  rename(Degree_unw_und = Degree.x) %>%
  rename(Degree_w_d = Degree.y)

# encode roles: Major = 3, Minor = 2, Extra = 1 (Major is 3 since higher role should have higher centrality)
combined_df$RoleNumeric <- as.numeric(recode_factor(combined_df$Role,
                                  "Extra" = 1, "Minor" = 2, "Major" = 3))

# Spearman correlations (between role and centralities)
print(cor.test(combined_df$RoleNumeric, combined_df$Degree_unw_und, method = "spearman"))
print(cor.test(combined_df$RoleNumeric, combined_df$Betweenness, method = "spearman"))
print(cor.test(combined_df$RoleNumeric, combined_df$Eigenvector, method = "spearman"))
print(cor.test(combined_df$RoleNumeric, combined_df$Closeness, method = "spearman"))

# Spearman correlations (between weighted and directed degree with centralities)
print(cor.test(combined_df$Degree_w_d, combined_df$Degree_unw_und, method = "spearman"))
print(cor.test(combined_df$Degree_w_d, combined_df$Betweenness, method = "spearman"))
print(cor.test(combined_df$Degree_w_d, combined_df$Eigenvector, method = "spearman"))
print(cor.test(combined_df$Degree_w_d, combined_df$Closeness, method = "spearman"))

# Kendall correlations (between role and centralities)
print(cor.test(combined_df$RoleNumeric, combined_df$Degree_unw_und, method = "kendall"))
print(cor.test(combined_df$RoleNumeric, combined_df$Betweenness, method = "kendall"))
print(cor.test(combined_df$RoleNumeric, combined_df$Eigenvector, method = "kendall"))
print(cor.test(combined_df$RoleNumeric, combined_df$Closeness, method = "kendall"))

# Kendall correlations (between weighted and directed degree with centralities)
print(cor.test(combined_df$Degree_w_d, combined_df$Degree_unw_und, method = "kendall"))
print(cor.test(combined_df$Degree_w_d, combined_df$Betweenness, method = "kendall"))
print(cor.test(combined_df$Degree_w_d, combined_df$Eigenvector, method = "kendall"))
print(cor.test(combined_df$Degree_w_d, combined_df$Closeness, method = "kendall"))
```

### Null Configuration Model

```{r null configuration model}

# degree sequence of the observed network
real_net_deg <- degree(series_adj_undirected, gmode = "graph")

set.seed(10)

# number of simulations
num_sims <- 1000  

# node names to help with value alignments
node_names <- V(series_net_undirected)$name
number_of_nodes <- length(node_names)

# initialise storage for the generated null model metrics
null_degrees <- matrix(NA, nrow = number_of_nodes, ncol = num_sims)
null_betweenness <- matrix(NA, nrow = number_of_nodes, ncol = num_sims)
null_closeness <- matrix(NA, nrow = number_of_nodes, ncol = num_sims)
null_eigen <- matrix(NA, nrow = number_of_nodes, ncol = num_sims)

null_transitivity <- numeric(num_sims)
null_avg_path_length <- numeric(num_sims)

# run 1000 simulations 
for (i in 1:num_sims) {
    null_net <- sample_degseq(real_net_deg, method = "simple.no.multiple")
    
    V(null_net)$name <- node_names
    
    deg_vals <- degree(as.matrix(get.adjacency(null_net)), gmode = "graph", rescale = TRUE)
    names(deg_vals) <- V(series_net_undirected)$name
    null_degrees[, i] <- deg_vals[node_names]
    
    eigen_vals <- eigen_centrality(null_net)$vector
    null_eigen[, i] <- eigen_vals[node_names]
    
    btwn_vals <- betweenness.estimate(null_net, directed = FALSE, cutoff = -1)
    null_betweenness[, i] <- btwn_vals[node_names]
    
    close_vals <- closeness.estimate(null_net, mode = "all", cutoff = -1)
    null_closeness[, i] <- close_vals[node_names]
      
    null_transitivity[i] <- transitivity(null_net, type = "global")
    null_avg_path_length[i] <- mean_distance(null_net, directed = FALSE)
}

# mean and std dev
null_degree_mean <- rowMeans(null_degrees)
null_degree_sd <- apply(null_degrees, 1, sd)

null_eigen_mean <- rowMeans(null_eigen)
null_eigen_sd <- apply(null_eigen, 1, sd)

null_betweenness_mean <- rowMeans(null_betweenness)
null_betweenness_sd <- apply(null_betweenness, 1, sd)

null_closeness_mean <- rowMeans(null_closeness)
null_closeness_sd <- apply(null_closeness, 1, sd)

null_transitivity_mean <- mean(null_transitivity)
null_transitivity_sd <- sd(null_transitivity)

null_avg_path_length_mean <- mean(null_avg_path_length)
null_avg_path_length_sd <- sd(null_avg_path_length)

# real network metrics
real_net_degree <- degree(series_adj_undirected, gmode = "graph", rescale = TRUE)
real_net_eigen <- eigen_centrality(series_net_undirected)$vector
real_net_betweenness <- betweenness.estimate(series_net_undirected, directed = FALSE, cutoff = -1)
real_net_closeness <- closeness.estimate(series_net_undirected, mode = "all", cutoff = -1)
real_net_transitivity <- transitivity(series_net_undirected, type = "global")
real_net_avg_path_length <- mean_distance(series_net_undirected, directed = FALSE)

# function to compute p-values and percentiles of each character for each centrality
compute_stats <- function(null_matrix, observed_vector) {
  
  n_sim <- ncol(null_matrix) # number of simulations = 1000
  
  p_upper <- numeric(nrow(null_matrix)) # nrows are the number of characters
  p_lower <- numeric(nrow(null_matrix))
  percentiles <- numeric(nrow(null_matrix))
  
  for (i in 1:nrow(null_matrix)) {
    
    null_vals <- null_matrix[i, ] # values for one particular character 
    obs <- observed_vector[i]
    
    # empirical p-value (upper tail)
    p_upper[i] <- (sum(null_vals >= obs) + 1) / (n_sim + 1)
    
    # empirical p-value (lower tail)
    p_lower[i] <- (sum(null_vals <= obs) + 1) / (n_sim + 1)
    
    # percentile (position in distribution)
    percentiles[i] <- (sum(null_vals <= obs) / n_sim) * 100
  }
  
  return(list(p_upper = p_upper, p_lower = p_lower, percentile = percentiles))
}

degree_stats <- compute_stats(null_degrees, real_net_degree)
eigen_stats <- compute_stats(null_eigen, real_net_eigen)
betweenness_stats <- compute_stats(null_betweenness, real_net_betweenness)
closeness_stats <- compute_stats(null_closeness, real_net_closeness)

# create dataframe
centrality_df <- data.frame(
    Name = node_names,
    
    Observed_Degree = real_net_degree,
    Null_Degree_Mean = null_degree_mean,
    Null_Degree_SD = null_degree_sd,
    
    Observed_Eigen = real_net_eigen,
    Null_Eigen_Mean = null_eigen_mean,
    Null_Eigen_SD = null_eigen_sd,
    
    Observed_Betweenness = real_net_betweenness,
    Null_Betweenness_Mean = null_betweenness_mean,
    Null_Betweenness_SD = null_betweenness_sd,
    
    Observed_Closeness = real_net_closeness,
    Null_Closeness_Mean = null_closeness_mean,
    Null_Closeness_SD = null_closeness_sd
)

# add p-values and percentiles
p_percentile_centrality_df <- centrality_df %>%
  mutate(
    Degree_p_upper = degree_stats$p_upper,
    Degree_p_lower = degree_stats$p_lower,
    Degree_percentile = degree_stats$percentile,
    
    Eigen_p_upper = eigen_stats$p_upper,
    Eigen_p_lower = eigen_stats$p_lower,
    Eigen_percentile = eigen_stats$percentile,
    
    Betweenness_p_upper = betweenness_stats$p_upper,
    Betweenness_p_lower = betweenness_stats$p_lower,
    Betweenness_percentile = betweenness_stats$percentile,
    
    Closeness_p_upper = closeness_stats$p_upper,
    Closeness_p_lower = closeness_stats$p_lower,
    Closeness_percentile = closeness_stats$percentile
  )

null_results_table <- bind_rows(
  p_percentile_centrality_df %>%
    select(Name, Observed = Observed_Degree, Null_Mean = Null_Degree_Mean, Null_SD = Null_Degree_SD, Percentile = Degree_percentile, P_Upper = Degree_p_upper, P_Lower = Degree_p_lower) %>% 
    mutate(Centrality = "Degree"),
  
  p_percentile_centrality_df %>%
    select(Name, Observed = Observed_Eigen, Null_Mean = Null_Eigen_Mean, Null_SD = Null_Eigen_SD, Percentile = Eigen_percentile, P_Upper = Eigen_p_upper, P_Lower = Eigen_p_lower) %>%
    mutate(Centrality = "Eigenvector"),
  
  p_percentile_centrality_df %>%
    select(Name, Observed = Observed_Betweenness, Null_Mean = Null_Betweenness_Mean, Null_SD = Null_Betweenness_SD, Percentile = Betweenness_percentile, P_Upper = Betweenness_p_upper, P_Lower = Betweenness_p_lower) %>%
    mutate(Centrality = "Betweenness"),
  
  p_percentile_centrality_df %>%
    select(Name, Observed = Observed_Closeness, Null_Mean = Null_Closeness_Mean, Null_SD = Null_Closeness_SD, Percentile = Closeness_percentile, P_Upper = Closeness_p_upper, P_Lower = Closeness_p_lower) %>%
    mutate(Centrality = "Closeness")
)

print(null_results_table)
write.csv(null_results_table, "series_null_results_table.csv", row.names = FALSE)

i <- which(V(series_net_undirected)$name == "Opah")

obs <- real_net_closeness[i]
null_vals <- null_closeness[i, ]

summary(null_vals)
obs
max(null_vals)

# reshape the data for all centrality measures
centrality_long <- centrality_df %>%
    pivot_longer(cols = c(Observed_Degree, Null_Degree_Mean,
                          Observed_Eigen, Null_Eigen_Mean,
                          Observed_Betweenness, Null_Betweenness_Mean,
                          Observed_Closeness, Null_Closeness_Mean),
                 names_to = "Type", values_to = "Value") %>%
    mutate(Centrality = case_when(
        Type %in% c("Observed_Degree", "Null_Degree_Mean") ~ "Degree",
        Type %in% c("Observed_Eigen", "Null_Eigen_Mean") ~ "Eigenvector",
        Type %in% c("Observed_Betweenness", "Null_Betweenness_Mean") ~ "Betweenness",
        Type %in% c("Observed_Closeness", "Null_Closeness_Mean") ~ "Closeness"
    ),
    Type = ifelse(grepl("Observed", Type), "Observed", "Null Model")) 


plot_centrality <- function(df, centrality_type, null_mean_col, null_sd_col, y_label) {
    # filter for the type of centrality measurw
    df_filtered <- df %>% filter(Centrality == centrality_type)

    # extract null model mean and standard deviation for error bars
    null_filtered <- centrality_df %>%
        select(Name, all_of(null_mean_col), all_of(null_sd_col)) %>%
        rename(Null_Mean = !!sym(null_mean_col), Null_SD = !!sym(null_sd_col)) %>%
        filter(!is.na(Null_SD))  # ensure that there are no missing values in SD

    # shape is circle for observed values, and square for null model values
    df_filtered <- df_filtered %>%
      mutate(Shape = ifelse(Type == "Observed", 16, 15))
    
    ggplot() +
        # observed and null values as points
        geom_point(data = df_filtered, aes(x = Name, y = Value, color = Type, shape = Type), size = 3) +
        
        # error bars for null model (Mean ± SD)
        geom_errorbar(data = null_filtered, aes(x = Name, 
                                                ymin = Null_Mean - Null_SD, 
                                                ymax = Null_Mean + Null_SD), 
                      width = 0.3, color = "black", linewidth = 0.3) +
      
        
        # set colour and shape of points
        scale_color_manual(values = c("blue", "red")) +      
        scale_shape_manual(values = c(16, 15)) +
        
        # labels and formatting
        labs(x = "Series Characters", y = y_label, color = "Type", shape = "Type") +
        theme_minimal(base_family = "sans") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 15),
              axis.text.y = element_text(size = 15),
              axis.title.x = element_text(size = 15),
              axis.title.y = element_text(size = 15),
              panel.grid = element_blank(),
              panel.border = element_blank(),
              axis.line = element_line(color = "black"),
              legend.title = element_text(size = 15),
              legend.text = element_text(size = 15))
}


# function to save png
save_null_plot <- function(df, centrality_type, null_mean_col, null_sd_col, y_label, filename) {
  
  # generate the plot
  p <- plot_centrality(df, centrality_type, null_mean_col, null_sd_col, y_label)
  
  # save PNG
  png(filename, width = 8.5, height = 7.5, units = "in", res = 1200, family = "sans")
  
  print(p)
  
  dev.off()
}


# generate plots for all centrality measures and save as png
#save_null_plot(centrality_long, "Degree", "Null_Degree_Mean", "Null_Degree_SD", "Degree Centrality", "Fig3(a).png")

save_null_plot(centrality_long, "Eigenvector", "Null_Eigen_Mean", "Null_Eigen_SD", "Eigenvector Centrality", "Fig3(a).png")

save_null_plot(centrality_long, "Betweenness", "Null_Betweenness_Mean", "Null_Betweenness_SD", "Betweenness Centrality", "Fig3(b).png")

save_null_plot(centrality_long, "Closeness", "Null_Closeness_Mean", "Null_Closeness_SD", "Closeness Centrality", "Fig3(c).png")
```

### Perturbation-Based Robustness Check

#```{r perturbation}

# # edge list with directed edges 
# edge_dir_df <- as.data.frame(edges_dir)
# 
# set.seed(10)
# 
# flip_edges <- function(edge_df, flip_frac = 0.05) {
#     
#   # define low-frequency edges, those with weight below the 25th percentile
#   weight_threshold <- quantile(edge_df$Weight, probs = 0.25)
#   
#   # obtain the df with only low-frequency
#   candidates <- edge_df %>%
#   filter(Weight <= weight_threshold)
#   
#   # obtain the number of edges to flip
#   n_flip <- ceiling(flip_frac* nrow(candidates))
#   
#   # randomly select edges to flip from the candidates df
#   flip_idx <- sample(seq_len(nrow(candidates)), n_flip)
#   
#   flipped <- candidates[flip_idx, ] # the rows to flip
#   
#   # swap Source and Target in df
#   chosen_flip <- flipped
#   chosen_flip$Source <- flipped$Target
#   chosen_flip$Target <- flipped$Source
#   
#   # remove the randomly chosen edges from the original df
#   removed_df <- anti_join(edge_df, flipped, by = c("Source", "Target", "Weight"))
#   
#   # add the flipped edges to the original df
#   perturbed_df <- bind_rows(removed_df, chosen_flip)
#   
#   return(perturbed_df)
# }
# 
# # store the original results in orig_roles
# orig_adj <- as.matrix(get.adjacency(series_net, attr = "Weight"))
# orig_deg <- degree(orig_adj, rescale = TRUE)
# names(orig_deg) <- V(series_net)$name
# orig_rank <- rank(-orig_deg, ties.method = "average")
# orig_roles <- role_df_corr[, c("Name", "Role")]
# 
# #####################
# 
# n_sims <- 1000 # number of simulations
# flip_frac <- 0.05 # fraction of low frequency edges to flip
# 
# rank_cor <- numeric(n_sims) # rank correlation for each simulation
# role_match <- numeric(n_sims)
# 
# for (i in 1:n_sims) {
#   
#   # perturb edge list
#   pert_edges <- flip_edges(edge_dir_df, flip_frac)
#   
#   # generate network
#   g_pert <- graph_from_data_frame(pert_edges, vertices = nodes, directed = TRUE)
#   adj_pert <- as.matrix(get.adjacency(g_pert, attr = "Weight"))
#   
#   # recompute degree
#   deg_pert <- degree(adj_pert, rescale = TRUE) # directed and weighted
#   names(deg_pert) <- V(g_pert)$name
#   pert_rank <- rank(-deg_pert, ties.method = "average")
#   
#   # get an order of nodes that appear in both the original and perturbed network
#   common_nodes <- intersect(names(orig_rank), names(pert_rank))
# 
#   # obtained the ranked correlation (in the same node order)
#   rank_cor[i] <- cor(orig_rank[common_nodes], pert_rank[common_nodes], method = "spearman")
#   
#   # Check assigned role stability
#   # get the perturbed list of nodes in descending order of directed and weighted degree
#   deg_df_pert <- data.frame(Name = names(deg_pert), Degree = deg_pert, row.names = NULL) %>% arrange(desc(Degree))
#   
#   # get average directed and weighted degree
#   avg_deg_pert <- mean(deg_df_pert$Degree)
#   # those with value less than average is Extra
#   deg_df_pert$Role <- ifelse(deg_df_pert$Degree < avg_deg_pert, "Extra", "Minor")
#   
#   # assign the Minor and Major roles according to classification criteria
#   gaps <- abs(diff(deg_df_pert$Degree[deg_df_pert$Role != "Extra"]))
#   if (length(gaps) > 0) {
#     max_gap <- which.max(gaps)
#     deg_df_pert$Role[1:max_gap] <- "Major"
#   }
#   
#   # put each characters' original and perturbed roles side by side
#   merged_roles <- merge(orig_roles, deg_df_pert[, c("Name", "Role")],
#                         by = "Name", suffixes = c("_orig", "_pert"))
#   
#   # get the percentage of role match 
#   role_match[i] <- mean(merged_roles$Role_orig == merged_roles$Role_pert)
# }
# 
# summary(rank_cor)
# summary(role_match)
# 
# median(rank_cor)
# mean(role_match)
# 
# #################### OUT DEGREE ################################################
# 
# orig_out <- degree(orig_adj, cmode = "outdegree", rescale = TRUE)
# names(orig_out) <- V(series_net)$name
# orig_out_rank <- rank(-orig_out, ties.method = "average")
# 
# out_rank_cor <- numeric(n_sims)
# 
# for (i in 1:n_sims) {
#   
#   # perturb edge list
#   pert_edges <- flip_edges(edge_dir_df, flip_frac)
#   
#   # generate network
#   g_pert <- graph_from_data_frame(pert_edges, vertices = nodes, directed = TRUE)
#   adj_pert <- as.matrix(get.adjacency(g_pert, attr = "Weight"))
#   
#   deg_pert_out <- degree(adj_pert, cmode = "outdegree", rescale = TRUE)
#   names(deg_pert_out) <- V(g_pert)$name
#   pert_out_rank <- rank(-deg_pert_out, ties.method = "average")
#   
#   common_nodes <- intersect(names(orig_out_rank), names(pert_out_rank))
#   
#   out_rank_cor[i] <- cor(orig_out_rank[common_nodes], pert_out_rank[common_nodes], method = "spearman")}
# 
# summary(out_rank_cor)
# 
# 
# #################### IN DEGREE ################################################
# 
# orig_in <- degree(orig_adj, cmode = "indegree", rescale = TRUE)
# names(orig_in) <- V(series_net)$name
# orig_in_rank <- rank(-orig_in, ties.method = "average")
# 
# in_rank_cor <- numeric(n_sims)
# 
# for (i in 1:n_sims) {
#   
#   # perturb edge list
#   pert_edges <- flip_edges(edge_dir_df, flip_frac)
#   
#   # generate network
#   g_pert <- graph_from_data_frame(pert_edges, vertices = nodes, directed = TRUE)
#   adj_pert <- as.matrix(get.adjacency(g_pert, attr = "Weight"))
#   
#   deg_pert_in <- degree(adj_pert, cmode = "indegree", rescale = TRUE)
#   names(deg_pert_in) <- V(g_pert)$name
#   pert_in_rank <- rank(-deg_pert_in, ties.method = "average")
#   
#   common_nodes <- intersect(names(orig_in_rank), names(pert_in_rank))
#   
#   in_rank_cor[i] <- cor(orig_in_rank[common_nodes], pert_in_rank[common_nodes], method = "spearman")}
# 
# summary(in_rank_cor)

#```

```{r perturbation part 2}

# edge list with directed edges 
edge_dir_df <- as.data.frame(edges_dir)

# PERTURBATION 1: FLIP EDGES
flip_edges <- function(edge_df, frac = 0.05) {
    
  # obtain the number of edges to flip
  n_flip <- ceiling(frac*nrow(edge_df))
  
  # randomly select edges to flip from the df
  flip_idx <- sample(seq_len(nrow(edge_df)), n_flip)
  
  flipped <- edge_df[flip_idx, ] # the rows to flip
  
  # swap Source and Target in df
  chosen_flip <- flipped
  chosen_flip$Source <- flipped$Target
  chosen_flip$Target <- flipped$Source
  
  # remove the randomly chosen edges from the original df
  removed_df <- edge_df[-flip_idx, ]
  
  # add the flipped edges to the original df
  flipped_perturbed_df <- bind_rows(removed_df, chosen_flip)
  
  return(flipped_perturbed_df)
}

# PERTURBATION 2: REMOVE EDGES
remove_edges <- function(edge_df, frac = 0.05) {
  
  n_remove <- ceiling(frac*nrow(edge_df)) # number of edges to remove
  remove_idx <- sample(seq_len(nrow(edge_df)), n_remove)
  
  removed_perturbed_df <- edge_df[-remove_idx, ] # simply remove those edges
  
  return(removed_perturbed_df)
}


# PERTURBATION 3: ADD EDGES
add_edges <- function(edge_df, nodes, frac = 0.05) {
  
  n_add <- ceiling(frac*nrow(edge_df))
  
  # the edges in df that we currently have as to avoid adding the same edges
  existing_edges <- paste(edge_df$Source, edge_df$Target)
  
  new_edges <- data.frame(Source = character(), Target = character(), 
                          Weight = numeric())
  
  while(nrow(new_edges) < n_add) {
    
    s <- sample(nodes$Name, 1)
    t <- sample(nodes$Name, 1)
    
    # if not self-loop and not an existing edge
    if (s != t && !(paste(s,t) %in% existing_edges)) {
      new_edges <- rbind(new_edges, data.frame(Source = s, Target = t,
                                               Weight = 1)) # adding a new edge gives weight 1
    }
  }
  
  added_perturbed_df <- bind_rows(edge_df, new_edges)
  
  return(added_perturbed_df)
}

# PERTURBATION 4: WEIGHT NOISE
weight_noise <- function(edge_df, frac = 0.05) {
  
  n_noise <- ceiling(frac*nrow(edge_df))
  noise_idx <- sample(seq_len(nrow(edge_df)), n_noise)
  
  for (i in noise_idx) {
    if (edge_df$Weight[i] == 1) {
      edge_df$Weight[i] <- edge_df$Weight[i] + 1 # increase the weight by 1 instead of subtracting to avoid edge deletion
    } else {
      edge_df$Weight[i] <- edge_df$Weight[i] + sample(c(-1,1), 1)
    }
  } 
  return(edge_df)
}

# PERTURBATION 5: COMBINATION OF ALL FOUR PERTURBATIONS
combined_perturb <- function(edge_df, nodes, frac = 0.05) {
  
  df <- edge_df
  
  n_edges <- nrow(df)
  n_total <- ceiling(frac*n_edges) # number of edges to perturb
  
  #________________________________
  # Choose edges to perturb
  #________________________________
  idx <- sample(seq_len(n_edges), n_total)
  
  #________________________________
  # split into 4 random proportions
  #________________________________
  props <- runif(4)
  props <- props/sum(props)
  
  sizes <- floor(props*n_total)
  
  # sum of sizes should be = n_total
  remainder <- n_total - sum(sizes)
  if (remainder > 0){
    add_idx <- sample(1:4, remainder, replace = FALSE)
    sizes[add_idx] <- sizes[add_idx] + 1
  }
  
  #________________________________
  # assign perturbation type to avoid perturbing the same edges over and over again
  #________________________________
  labels <- rep(c("flip", "remove", "noise", "add"), times = sizes)
  labels <- sample(labels)  # shuffle
  
  pert_map <- data.frame(idx = idx, type = labels)
  
  #________________________________
  # split the perturbations
  #________________________________
  
  noise_idx  <- pert_map$idx[pert_map$type == "noise"]
  flip_idx   <- pert_map$idx[pert_map$type == "flip"]
  remove_idx <- pert_map$idx[pert_map$type == "remove"]
  n_add      <- sum(pert_map$type == "add") # to obtain how many to add
  
  # save the original edges that are present to avoid adding the same edges later on
  existing_edges <- paste(df$Source, df$Target)
  
  #________________________________
  # apply perturbations (Noise -> Flip -> Remove -> Add)
  #________________________________
  
  # 1. Noise
  
  for (i in noise_idx) {
    if (df$Weight[i] == 1) {
      df$Weight[i] <- df$Weight[i] + 1
    } else {
      df$Weight[i] <- df$Weight[i] + sample(c(-1,1), 1)
    }
  }
  
  # 2. Flip
  df_flip <- df[flip_idx, ] # from the original df, get only the edges that are supposed to be flipped
  
  df_flip_new <- df_flip
  df_flip_new$Source <- df_flip$Target
  df_flip_new$Target <- df_flip$Source
  
  # 3. Removal
  # remove and flip in a single step (to avoid overlapping perturbations on the same edge)
  edges_to_remove <- unique(c(remove_idx, flip_idx))
  df <- df[-edges_to_remove, ]
  
  # re-add the flipped edges after removing the old directions
  df <- bind_rows(df, df_flip_new)
  
  # 4. Add
  new_edges <- data.frame(Source = character(), Target = character(),
                          Weight = numeric())
  
  while(nrow(new_edges) < n_add) {
    
    s <- sample(nodes$Name, 1)
    t <- sample(nodes$Name, 1)
    
    if (s != t && !(paste(s,t) %in% existing_edges)) {
      new_edges <- rbind(new_edges,
                         data.frame(Source = s, Target = t, Weight = 1))
      
    }
  }
  
  df <- bind_rows(df, new_edges)
  
  return(df)
  
}

#___________________________________________________________________
# store the original results in orig_roles
orig_adj <- as.matrix(get.adjacency(series_net, attr = "Weight"))
orig_deg <- degree(orig_adj, rescale = TRUE)
names(orig_deg) <- V(series_net)$name
orig_rank <- rank(-orig_deg, ties.method = "average")
orig_roles <- role_df_corr[, c("Name", "Role")]

# original results for out-degree
orig_out <- degree(orig_adj, cmode = "outdegree", rescale = TRUE)
names(orig_out) <- V(series_net)$name
orig_out_rank <- rank(-orig_out, ties.method = "average")

# original results for in-degree
orig_in <- degree(orig_adj, cmode = "indegree", rescale = TRUE)
names(orig_in) <- V(series_net)$name
orig_in_rank <- rank(-orig_in, ties.method = "average")

#####################

run_simulation <- function(perturb_function, edge_df, nodes, frac, n_sims = 1000){
  
  rank_corr <- numeric(n_sims) # rank correlation for each simulation
  role_match <- numeric(n_sims)
  out_rank_corr <- numeric(n_sims)
  in_rank_corr <- numeric(n_sims)
  
  for (i in 1:n_sims) {
  
    # perturb edge list
    pert_edges <- perturb_function(edge_df, nodes, frac)
    
    # generate network of the perturbed edge list
    g_pert <- graph_from_data_frame(pert_edges, vertices = nodes, directed = TRUE)
    adj_pert <- as.matrix(get.adjacency(g_pert, attr = "Weight"))
    
    #_________________________
    # OVERALL DEGREE
    #_________________________
    
    # recompute degree
    deg_pert <- degree(adj_pert, rescale = TRUE) # directed and weighted
    names(deg_pert) <- V(g_pert)$name
    pert_rank <- rank(-deg_pert, ties.method = "average")
    
    # get an order of nodes that appear in both the original and perturbed network
    common_nodes <- intersect(names(orig_rank), names(pert_rank))
  
    # obtained the ranked correlation (in the same node order)
    rank_corr[i] <- cor(orig_rank[common_nodes], pert_rank[common_nodes], method = "spearman") # ranked corr of simulation i
    
    # Check assigned role stability
    # get the perturbed list of nodes in descending order of directed and weighted degree
    deg_df_pert <- data.frame(Name = names(deg_pert), Degree = deg_pert, row.names = NULL) %>% arrange(desc(Degree))
    
    # get average directed and weighted degree
    avg_deg_pert <- mean(deg_df_pert$Degree)
    # those with value less than average is Extra
    deg_df_pert$Role <- ifelse(deg_df_pert$Degree < avg_deg_pert, "Extra", "Minor")
    
    # assign the Minor and Major roles according to classification criteria
    gaps <- abs(diff(deg_df_pert$Degree[deg_df_pert$Role != "Extra"]))
    if (length(gaps) > 0) {
      max_gap <- which.max(gaps)
      deg_df_pert$Role[1:max_gap] <- "Major"
    }
    
    # put each characters' original and perturbed roles side by side
    merged_roles <- merge(orig_roles, deg_df_pert[, c("Name", "Role")],
                          by = "Name", suffixes = c("_orig", "_pert"))
    
    # get the percentage of role match 
    role_match[i] <- mean(merged_roles$Role_orig == merged_roles$Role_pert)
    
    #______________________________
    # OUT-DEGREE
    #______________________________
    
    deg_pert_out <- degree(adj_pert, cmode = "outdegree", rescale = TRUE)
    names(deg_pert_out) <- V(g_pert)$name
    pert_out_rank <- rank(-deg_pert_out, ties.method = "average")
    
    common_nodes_out <- intersect(names(orig_out_rank), names(pert_out_rank))
    
    out_rank_corr[i] <- cor(orig_out_rank[common_nodes_out],
                            pert_out_rank[common_nodes_out], 
                            method = "spearman")
    
    # _________________________________
    # IN-DEGREE
    #__________________________________
    
    deg_pert_in <- degree(adj_pert, cmode = "indegree", rescale = TRUE)
    names(deg_pert_in) <- V(g_pert)$name
    pert_in_rank <- rank(-deg_pert_in, ties.method = "average")
    
    common_nodes_in <- intersect(names(orig_in_rank), names(pert_in_rank))
    
    in_rank_corr[i] <- cor(orig_in_rank[common_nodes_in],
                           pert_in_rank[common_nodes_in], method = "spearman")
  }
  
  return(data.frame(
    median_rank_corr = median(rank_corr),
    mean_role_match = mean(role_match),
    median_out_rank_corr = median(out_rank_corr),
    median_in_rank_corr = median(in_rank_corr)
  ))
}


noise_wrap <- function(df, nodes, frac) {
  weight_noise(df, frac)
}

flip_wrap <- function(df, nodes, frac) {
  flip_edges(df, frac)
}

remove_wrap <- function(df, nodes, frac) {
  remove_edges(df, frac)
}

add_wrap <- function(df, nodes, frac) {
  add_edges(df, nodes, frac)
}

combined_wrap <- function(df, nodes, frac){
  combined_perturb(df, nodes, frac)
}

set.seed(123)

fracs <- c(0.05, 0.10, 0.50, 0.90)

results <- do.call(rbind, lapply(fracs, function(f) {
  rbind(
    cbind(type = "noise", frac = f, run_simulation(noise_wrap, edge_dir_df, nodes, f)),
    cbind(type = "flip", frac = f, run_simulation(flip_wrap, edge_dir_df, nodes, f)),
    cbind(type = "remove", frac = f, run_simulation(remove_wrap, edge_dir_df, nodes, f)),
    cbind(type = "add", frac = f, run_simulation(add_wrap, edge_dir_df, nodes, f)),
    cbind(type = "combined", frac = f, run_simulation(combined_wrap, edge_dir_df, nodes, f))
  )
}))

print(results)

```
